### 2009-12-17 docs/marcello-dissertation/thesis/chapter8-experimental-results-correct-behavior-and-performance.tex
Fixing the header of the table of the operations. Replacing "Insert" by "Create" to follow the pattern CRUD (Create, ...)
git-svn-id: svn://localhost/netbeams/branches/marcello/persistence@712 559edde2-a4d4-44e0-96fc-4035e40d7396
Feedback from Prof. Murphy after the presentation, adding the hardware specifications.
git-svn-id: svn://localhost/netbeams/branches/marcello/persistence@718 559edde2-a4d4-44e0-96fc-4035e40d7396

\begin{table}[!h]
    \begin{center}
        \begin{tabular}{|c|c|c|c|}\hline
        \textbf{Scenario Type} & \textbf{Language} & \textbf{Method Call} & \textbf{Use Case}\\\hline 
        \textbf{Insert} & Java & db.SondeDataContainer.insert() & R0\\\hline
        \textbf{Retrive} & Javascript & db.SondeDataContainer.find() & R1, R2, R3\\\hline 
        \textbf{Update} & Javascript & db.SondeDataContainer.update() & U1\\\hline 
        \textbf{Delete} & Javascript & db.SondeDataContainer.remove() & D1\\\hline
        \textbf{Export} & Python & db.SondeDataContainer.find() & R4\\\hline
        \end{tabular}
        \caption{mongoDB method calls used for the use cases}
    \end{center}
    \label{tab:experiment-scenarios-mongo-methods}
\end{table}

@@

Different problems and limitations were faced during the execution of
mongoDB, which were related to the infrastructure used: the limitations
regarding disk storage in 32bit operating systems and very slow
performance when using virtualized servers. During the execution of the
experiments, mongoDB used memory accordingly, without taking control of the
operating system's resources. However, when mongoDB is used in a 32bit server
architecture, there are limitations on the disk space used to store
collections. After reaching 2GB of collected data during many different runs,
mongoDB crashed and did not allow the use of the collected data. For this
reason, the setup of a new VirtualBox using Ubuntu Linux 64bits as a guest to
a Mac OS X 64bits was prepared and used throughout the completion of these
experiments. On the other hand, the performance was drastically decreased 
using mongoDB in virtualized servers due to the fact of dynamic partition
chosen. The performance shell application ``iostat'' was used to verify the
behavior, and the use of mongoDB was switched to the host operating system.

>>>>

\begin{table}[!h]
    \begin{center}
        \begin{tabular}{|c|c|c|c|}\hline
        \textbf{Scenario Type} & \textbf{Language} & \textbf{Method Call} & \textbf{Use Case}\\\hline 
        \textbf{Create} & Java & db.SondeDataContainer.insert() & R0\\\hline
        \textbf{Retrive} & Javascript & db.SondeDataContainer.find() & R1, R2, R3\\\hline 
        \textbf{Update} & Javascript & db.SondeDataContainer.update() & U1\\\hline 
        \textbf{Delete} & Javascript & db.SondeDataContainer.remove() & D1\\\hline
        \textbf{Export} & Python & db.SondeDataContainer.find() & R4\\\hline
        \end{tabular}
        \caption{mongoDB method calls used for the use cases}
    \end{center}
    \label{tab:experiment-scenarios-mongo-methods}
\end{table}

@@

Different problems and limitations were faced during the execution of
mongoDB, which were related to the infrastructure used: the limitations
regarding disk storage in 32bit operating systems and very slow
performance when using virtualized servers. During the execution of the
experiments, mongoDB used memory accordingly, without taking control of the
operating system's resources. However, when mongoDB is used in a 32bit server
architecture, there are limitations on the disk space used to store
collections. After reaching 2GB of collected data during many different runs,
mongoDB crashed and did not allow the use of the collected data. For this
reason, the setup of a new VirtualBox using Ubuntu Linux 64bits as a guest to
a Mac OS X 64bits was prepared and used throughout the completion of these
experiments. On the other hand, the performance was drastically decreased 
using mongoDB in virtualized servers due to the fact of dynamic partition
chosen. The performance shell application ``iostat'' was used to verify the
behavior, and the use of mongoDB was switched to the host operating system,
whose hardware specifications are summarized on Table \ref{tab:mac-os-setup}.

\begin{table}[!h] 
    \label{tab:mac-os-setup}
    \caption{Experiment Host Machine Hardware Specifications}
    \begin{center}
        \begin{tabular}{|c|c|}\hline 
        \textbf{Model Name} &  MacBook Pro\\\hline
        \textbf{Model Identifier} & MacBookPro5,3\\\hline 
        \textbf{Processor Name} & Intel Core 2 Duo\\\hline 
        \textbf{Processor Speed} & 2.66 GHz\\\hline 
        \textbf{Number Of Processors} & 1\\\hline 
        \textbf{Total Number Of Cores} & 2\\\hline 
        \textbf{L2 Cache} & 3 MB\\\hline 
        \textbf{Memory} & 8 GB\\\hline 
        \textbf{Bus Speed} & 1.07 GHz\\\hline
        \end{tabular}
    \end{center}
\end{table}
